\MakeUppercase{Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-15 k-planar.tex
Fixed v in S_x versus v in S_{x'} issue

  Refer to \figref{A}(b)
  If $B_x$ contains some $K$-ancestor $a_i$, $i\in\{0,\ldots,d-1\}$, of $x$, it is because there is an edge $vw\in E(G)$ with $v\in S_x$ and $w\in S_{a_i}$.  The edge $vw$ corresponds to a walk $W_{vw}$ in $G^+$. The walk $W_{vw}$ is contained in $N_x-F_x$, otherwise $x\not\in A_{vw}$ so $x\not\in A_v$, and $a(v)\neq x$, contradicting the fact that $v\in S_x$.

  However, $w\in S_{_i}$, so there exists an edge $ww'\in E(G)$ such that   $W_{ww'}$ is contained in $W_{ww'}\subseteq N_{a_i}-F_{a_i}$ but $W_{ww'}\not\subseteq N_{a_{i+1}}-F_{a_{i+1}}$.  Therefore $W_{ww'}$ must contain a first vertex $w^*\in V(F_{a_{i+1}}-F_{a_{i}})\subseteq Y_{a_i}$.

>>>>

  Refer to \figref{A}(b)
  If $B_x$ contains some $K$-ancestor $a_i$, $i\in\{0,\ldots,d-1\}$, of $x$, it is because there is an edge $vw\in E(G)$ with $w\in S_{a_i}$ and $v\in S_{x'}$ for some $K$-descendant of $x$.  The edge $vw$ corresponds to a walk $W_{vw}$ in $G^+$. The walk $W_{vw}$ is contained in $N_x-F_x$, otherwise $x\not\in A_{vw}$ so $x'\not\in A_{vw}$, so $x'\not\in A_v$, and $a(v)\neq x'$, contradicting the fact that $v\in S_{x'}$.

  However, $w\in S_{a_i}$, so there exists an edge $ww'\in E(G)$ such that   $W_{ww'}$ is contained in $W_{ww'}\subseteq N_{a_i}-F_{a_i}$ but $W_{ww'}\not\subseteq N_{a_{i+1}}-F_{a_{i+1}}$.  Therefore $W_{ww'}$ must contain a first vertex $w^*\in V(F_{a_{i+1}}-F_{a_{i}})\subseteq Y_{a_i}$.
